---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data

The Behavioral Risk Factor Surveillance System (BRFSS) is the nation’s premier system of health-related telephone surveys that collect state data about U.S. residents regarding their health-related risk behaviors, chronic health conditions, and use of preventive services. 

Data is collected from all 50 states as well as the District of Columbia, Guam, Puerto Rico, and the U.S. Virgin Islands. BRFSS is the largest continuously conducted health survey system in the world.

## Sample

The BRFSS is administered and supported by CDC’s Population Health. Obtaining samples of telephone numbers from CDC.

The samples were collected by:

- landline telephone survey: interviewers collect data from a randomly selected adult in a household.

- cell-phones telephonic surveys: interviewers collect data from an adult who participates by using a cellular telephone and resides in a private residence or college housing.
Disproportionate stratified sampling was used for land-line telephones. And the cellular phone sample is randomly generated from the combination od area code and prefix.


## Inference

If we look at the sample collection methods, we would conclude that this is an observational study. It uses stratified sampling method based on random digit dialing methods.

## Generalizability

The observational study is generalize to all adults non-institutionalized (18-years and older).

## Causality

As this is an observational study we can only be sure of  correlation/association, not a causation.

* * *
names(brfss2013.RData)

## Part 2: Research questions

**Research quesion 1:**
How does the Type Of Physical Activity affect physhlth and menthlth.

physhlth: Number Of Days Physical Health Not Good
menthlth: Number Of Days Mental Health Not Good
exract11: Type Of Physical Activity

Is there a correlation between variable (exract11) (physhlth) and (menthlth).
This would be a preliminary data exploration to examine the question How the type of Activity affect mental and physical 
Health.

**Research quesion 2:**
How does the Tobacco Use affect the General Health

smoke100: Smoked At Least 100 Cigarettes
genhlth: General Health

It would be interesting to know about how Smoked At Least 100 Cigarettes affect the general health of a person.

**Research quesion 3:**
How does Sugar Drinks affect Pre-Diabetes

pdiabtst: Had A Test For High Blood Sugar In Past Three Years
prediab1: Ever Been Told You Have Pre-Diabetes Or Borderline Diabetes
ssbfrut2: How Often Did You Drink Sugar-Sweetened Drinks?

We can examine the correlation between comsumption of sugar drinks
and the probability of a person with pre-diabetes.

* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```

**Research quesion 2:**

```{r}

```


**Research quesion 3:**

```{r}

```

